---
title: "About Data Science HW1"
author: "AMJ"
format: html
editor: visual
---

### My Responses

Being a data scientist is about using your skills in mathematics and computer science to find patterns and solve problems using big data.

- Statisticians and data scientists both work to analyze and interpret large amounts of data.
- They both use statistical methods to come up with answers
- Data scientists might work more with the technical/software side to gather data while statisticians work more within the math space.

I view myself as a data scientist because I have a background in computer science so I'm fine with working with software. I also like working with math/statistics and that is all part of being a good data scientist.

### R Snippet

Here I am creating an object called 'y' within R as specified.

```{r}
y <- density(iris$Petal.Width)

class(y)
typeof(y)
str(y)
```

The code above is to determine the class, type, and structure of the object y.

```{r}
#| echo: false

plot(y)
```
You should see the plot but the code should not render!

